### 2015-07-12 narrative/naming-service.tex
more edits for clarity

\paragraph{Related Work:}
Structurally, the traditional POSIX naming service offering a hierarchical
space consisting of directories and files may be maintained for backwards
compatibility. However, this view will not offer the same strict semantics
POSIX defines. We must break these strict semantics to address scalability
problems forced by the serialized access to a single source for creating and
accessing files.  Several efforts~\cite{patil:2007:giga+,carns:pvfs} have
worked to reduce this contention by reducing the serialized
scope to a single directory or subtree or by allowing a single process in a
collective file operation talk with the metadata service and distribute a
handle to other participants. While these approaches help, they do not address
this key scalability limitation of serialized access - even if the metadata
service is spread across multiple nodes. Instead, we will offer a short
duration to consistency POSIX view to offer the performance and consistency
requirements an exascale application demands.

In pure object stores, such as those popular in the big data
domain~\cite{Fitzpatrick:2004:memcached}, one avoids this bottleneck by
strictly offering an object ID with the application required to manage how this
ID maps to something of interest. This approach of removing the metadata
service from the system level completely can work well for scaling out
applications where data is created or consumed by a single process at a time or
just in a work queue, rather than potentially O(1 million) processes all
actively requesting for a single ``object''. To address this case, having some
system integrated metadata services to associate names with these object is a
preferable solution. We will offer solutions to address legacy application and
command-line style data access and migration to other storage types using these
POSIX semantics, without providing the same synchronous consistency semantics
as POSIX.

\paragraph{Challenge:}
The main challenge of incorporating the additional, rich metadata will be
joined by the additional challenge of coordinating with the other storage and
application layer services to offer the best access times possible for data
stored in the system at available data quality levels. The developed metadata
services that drive data compression and subsetting operations must have easy,
consistent, and ideally non-blocking or locking access to this metadata
service. We must investigate how to build such a metadata and naming service
that also incorporates and maintains the additional metadata required to
support our advanced functionality.

>>>>

\paragraph{Related Work:}
Structurally, the traditional POSIX naming service offering a hierarchical
space consisting of directories and files may be maintained for backwards
compatibility. However, this view will not offer the same strict semantics
POSIX defines. We must break these strict semantics to address scalability
problems forced by the serialized access to a single source for creating and
accessing files.  Several efforts~\cite{patil:2007:giga+,carns:pvfs} have
worked to reduce this contention by reducing the serialized
scope to a single directory or subtree or by allowing a single process in a
collective file operation talk with the metadata service and distribute a
handle to other participants. While these approaches help, they do not address
this key scalability limitation of serialized access - even if the metadata
service is spread across multiple nodes. The problem is the centralized listing
of where file stripes are stored or other, similar information. Instead, we
will offer a short duration to consistency POSIX view to offer the performance
and consistency requirements an exascale application demands.

Pure object stores, such as those popular in the big data
domain~\cite{Fitzpatrick:2004:memcached}, avoid this bottleneck by only
offering an object ID and offloading the ID to name mapping to the application.
Removing the metadata service completely from the system level can work well
for scale-out applications where data is created or consumed by a single
process at a time or just in a work queue rather than potentially O(1 million)
processes all actively requesting a single ``object''. To address this case,
having some system integrated metadata services to associate names with object
and chunk IDs is a preferable solution. We will offer solutions to address
legacy application and command-line style data access and migration to other
storage types using these POSIX semantics, without providing the same
synchronous consistency semantics as POSIX.

\paragraph{Challenge:}
The main challenge of incorporating the additional, rich metadata will be
joined by coordinating with the other storage and
application layer services to offer the best access times possible for data
stored in the system at available data quality levels. The developed metadata
services that drive data compression and subsetting operations must have easy,
consistent, and ideally non-blocking or locking access to this metadata
service. We must investigate how to build such a metadata and naming service
that also incorporates and maintains the additional metadata required to
support our advanced functionality.
